lab_notebook

### 2018-12-04 lab_notebook.Rmd
glm Prob(ITQ) ~F(gdp, ISSCAAP)

@@

>>>>

#write.csv(gdp_rightsbased, file = "gdp_rightsbased.csv")

@@

######
MPA data wrangling
######
```{r}

ISO_country_codes <- read_excel("data/ISO_country_codes.xlsx")
MPA <- readRDS("data/WDPA_Nov2018.rds")

mpa_simple <- MPA %>%
  select("NAME", "PA_DEF", "DESIG_ENG", "DESIG_TYPE", "IUCN_CAT", "MARINE", "REP_M_AREA", "NO_TAKE", "STATUS", "PARENT_ISO3") %>%
  filter(MARINE != "0")

colnames(mpa_simple) <- c("NAME", "PA_DEF", "DESIG_ENG", "DESIG_TYPE", "IUCN_CAT", "MARINE", "REP_M_AREA", "NO_TAKE", "STATUS", "code")

mpa_join <- join(mpa_simple, ISO_country_codes, by = c("code"), type = "full")

mpa_updated <- mpa_join %>%
  select("Country", "NAME", "DESIG_ENG", "DESIG_TYPE", "IUCN_CAT", "MARINE", "REP_M_AREA", "NO_TAKE", "STATUS" ) %>%
  filter(NAME != "NA" & DESIG_ENG != "NA" & DESIG_TYPE != "NA" & IUCN_CAT != "NA" & MARINE != "NA" & REP_M_AREA != "NA" & NO_TAKE != "NA" & STATUS != "NA")

write.csv(mpa_updated, file = "mpa_updated.csv")

PA_DEF: Allowed values: 1 (meets IUCN and/or CBD PA definition); 0 (does not meet IUCN and/or CBD PA definition (currently stored outside WDPA)).

MARINE: Allowed values: 0 (100% Terrestrial PA), 1 (Coastal: marine and terrestrial PA), and 2 (100 % marine PA).
